---
title: "R Notebook"
output: html_notebook
---

#step0: load packages and specify directories
```{r}


```

#step1: load and process data
```{r}
AKumar <- data.frame(scan("AKumar.txt",
                          what = list(Coauthor = "", Paper = "", Journal = ""),
                          sep=">", quiet=TRUE), stringsAsFactors=F)
AKumar$clusterid <- sub("_.*","",AKumar$Coauthor)
AKumar$citationid <- sub(".*_(\\w*)\\s.*", "\\1", AKumar$Coauthor)
AKumar$coauthor <- gsub("<","",sub("^.*?\\s","", AKumar$Coauthor))
AKumar$Paper <- gsub("<","",AKumar$Paper)
AKumar$index <- rownames(AKumar)
```

```{r}
###################################### J Smith #################################
JSmith <- data.frame(scan("/Users/ouminamikun/Documents/Columbia/Spring 2017/ADS/Project 4/nameset/JSmith.txt",
                          what = list(coauthor ="", paper = "", publication =""),
                          sep = ">", quiet = T),stringsAsFactors = F)
JSmith$authors <- gsub("<","",sub("^.*?\\s","", JSmith$coauthor))
JSmith$clusterid <- sub("_.*","",JSmith$coauthor)
```

```{r}
authors <- strsplit(JSmith$authors, ";")
authors

##authors name frequencies table
freq_authors <- c(authors[[1]],authors[[2]])
for(i in 3:length(authors)){
   freq_authors<- c(freq_authors, authors[[i]])
}
freq_authors <- as.data.frame(sort(table(freq_authors)))
colnames( freq_authors) <- c("authors", "frequencies")

##number of authors for each citation
num_authors <- NA
for(i in 1:length(authors)){
  num_authors[i] <- length(authors[[i]])
}
JSmith$num_authors <- num_authors

clusterid_index <- unique(JSmith$clusterid)
```


```{r}
##No.10 J Smith
index <- JSmith$clusterid == clusterid_index[1]
p_id10 <- mean(index)
p_id10

#the prob of Xi writing a futrue paper alone conditioned on the event of Xi
p_N <- mean(JSmith$num_authors[index]==1)
p_co <- 1-p_N
```

```{r}
##authors name frequecies table
freq_authors_id10 <- c(authors_id10[[1]],authors_id10[[2]])
for(i in 3:length(authors_id10)){
   freq_authors_id10 <- c(freq_authors_id10, authors_id10[[i]])
}

freq_authors_id10 <- as.data.frame(sort(table(freq_authors_id10)))
colnames(freq_authors_id10) <- c("authors", "frequencies")

#the prob of Xi writing a futre paper with previously seen coauthors condiitoned on the event that Xi writes a futre paper with coauthors
authors_id10 <- authors[index]
authors_id10
sum(JSmith$num_authors[index] - 1) #total number of times Xi coauthors with any coauthor
p_seen_co <- (sum(c_authors_id10$Freq >= 2) - 1) / sum(JSmith$num_authors[index] - 1)
p_seen_co
p_unseen_co <- 1 - p_seen_co

```

```{r}
#the prob of Xi writing a future paper with a particular coauthor A1k conditioned on the event that X1 writes a paper with a previously seen coauthors
p_A11_seen_co <- freq_authors_id10[freq_authors_id10$authors == "Terence C Fogarty", "frequencies"]/sum(JSmith$num_authors[index] - 1)
p_A11_seen_co 
p_A11_unseen_co <- 1/ (nrow(freq_authors) - (nrow(freq_authors_id10) - 1))
```

```{r}
p_A11 <- p_A11_seen_co*p_seen_co*p_co + p_A11_unseen_co*p_unseen_co*p_co
log(p_A11) + log(p_id10)

```

```{r}
JSmith_features <- matrix(0, 225, 255)
JSmith_features[,1] <- JSmith$clusterid



for(i in 1:225){
  j_ind <- matrix(0, nrow =length(authors[[i]]), ncol = 254)
  for(j in 1:length(authors[[i]])){
    j_ind[j,] <- authors[[i]][j] == freq_authors$authors
  }
  JSmith_features[,-1][i,] <- as.numeric(colSums(j_ind))
}

which(JSmith_features[2,] == 1)
JSmith_features_id <- unique(JSmith_features[,1])

JSmith_features_id
###########################################################################################################
```

#Construct coauthors matrix
```{r}
#here: load M and cleanData

label <- function(data_list, num){
  nameset <- data_list[[num]]
  n <- length(nameset)
  label <- NA
  for(i in 1:n){
    label[i] <- nameset[[i]][1]
  }
  
  return(unlist(label))
}

labels <- NULL
for(i in 1:14){
  l <- label(data_list = data_list, num = i)
  labels[[i]] <- l
}

coauthors <- NULL
for(i in 1:14){
  obs <- length(data_list[[i]])
  d <- ncol(M[[i]])
  labels[[i]] <- as.matrix(labels[[i]])
  coauthors[[i]] <- cbind(labels[[i]],M[[i]][1:obs, (obs+1) : d])
  coauthors[[i]] <- cbind(coauthors[[i]], rep(1,obs))
}
```

#split data function
```{r}

split_data <- function(m){
    #input m = one class of one nameset
    #output = train and test data for that class
  
    obs <- nrow(m)
    index <- sample(1:obs,round(obs/2))
    train_data <- m[index,]
    test_data <- m[-index,]
    return(list(train_data = train_data, test_data = test_data))
}
```

#Split all nameset data into train and test data for 10 times and store them as cvs files
```{r}
#DON'T RUN THIS AGAIN!!!

###split every class in a nameset and for loop 14 namesets
s <- NULL
ss <- NULL
for(i in 1:14){
  s[[i]] <- split(as.data.frame(coauthors[[i]]), coauthors[[i]][,1])
  ss[[i]] <- lapply(s[[i]], split_data)
}

###combine train data of every class and for loop 14 namesets
train <- NULL
for(i in 1:14){
  n <- length(ss[[i]])
  train[[i]] <- ss[[i]][[1]]$train_data
  for(j in 2:n){
    train[[i]] <- rbind(train[[i]], ss[[i]][[j]]$train_data)
  }
}

for(i in 1:14){
  train_data_frame <- train[[i]]
  file_name <- paste("train_",i,".csv" ,sep = "")
  write.csv(train_data_frame, paste("/Users/ouminamikun/Documents/Columbia/Spring 2017/ADS/Spr2017-proj4-team-14/output/Exp10/", file_name,sep = ""), row.names = F)
}


###combine test data of every class and for loop 14 namesets
test <- NULL
for(i in 1:14){
  n <- length(ss[[i]])
  test[[i]] <- ss[[i]][[1]]$test_data
  for(j in 2:n){
    test[[i]] <- rbind(test[[i]], ss[[i]][[j]]$test_data)
  }
}

for(i in 1:14){
  test_data_frame <- test[[i]]
  file_name <- paste("test_",i,".csv" ,sep = "")
  write.csv(test_data_frame, paste("/Users/ouminamikun/Documents/Columbia/Spring 2017/ADS/Spr2017-proj4-team-14/output/Exp10/", file_name,sep = ""), row.names = F)
}
```

#train function
```{r}
nb_train <- function(train_x, train_y){
  
  d <- ncol(train_x)
  id <- unique(train_y)
  k <- length(id)
  P_No <- NA
  P_Co <- NA
  co_times <- matrix(NA, nrow = k, ncol = d)
    
  for(i in 1:k){
    ##prob of writing without coauthors and with ones
    row_sum <- rowSums(train_x)
    index <- train_y == id[i]
    row_sum_id <- row_sum[index]
    No_ind <- row_sum_id == 1
    P_No[i] <- mean(No_ind)
    P_Co[i] <- 1 - P_No[i]
    
    ##prob of wrting witho seen coauthors and without ones
    train_x_id <- train_x[index,]
    dimension <- ifelse(is.matrix(train_x_id), 2, 1)
    if(dimension == 1){
      co_times[i,] <- train_x_id
    }
    else if(dimension == 2){
      co_times[i,] <- colSums(train_x_id)
    }
  }
  co_times_omt<- co_times[, -d]
  seen_times <- apply(co_times_omt, 1, function(x){sum(x[x >= 2])})
  total_times <- rowSums(co_times_omt)
  P_Seen_Co <- seen_times / total_times
  P_Unseen_Co <- 1 - P_Seen_Co
  
  ##
  P_A1k_Seen_Co <- prop.table(co_times_omt, 1)
  P_A1k_Unseen_Co <- 1 / (sum(co_times_omt) - rowSums(co_times_omt))
  
  ##
  prop <- prop.table(co_times, 2)
  Prior <- prop[,d]
    
  return(list(Prior = Prior,
              P_No = P_No,
              P_Co = P_Co, 
              P_Seen_Co = P_Seen_Co, 
              P_Unseen_Co = P_Unseen_Co,
              P_A1k_Seen_Co = P_A1k_Seen_Co,
              P_A1k_Unseen_Co = P_A1k_Unseen_Co))
}


train_x <- as.matrix(train_1[,-1])
train_y <- train_1[,1]
model <- nb_train(train_x = train_x, train_y = train_y)
model
```

#test function
```{r}
nb_test <- function(model, test_data){
  
  n <- dim(test_data)[1]
  d <- dim(test_data)[2]
  test_data_omt <- test_data[,-d]
  K <- rowSums(test_data_omt)
  n_id <- length(model$Prior)
  posterior <- matrix(NA, nrow = n, ncol = n_id)
  class <- NA
  
  for(i in 1:n){
      N <- K[i]
      name_ind <- test_data_omt[i,] == 1
      for(j in 1:n_id){
        if(N == 0){
          posterior[i,j] <- model$P_No[j] * model$Prior[j]
        }
        else if(N >= 1){
          posterior[i,j] <- prod( model$P_A1k_Seen_Co[j, name_ind] * model$P_Seen_Co[j] * model$P_Co[j] +   rep(model$P_A1k_Unseen_Co[j], sum(name_ind)) * model$P_Unseen_Co[j] * model$P_Co[j]) * model$Prior[j]
        }
      }
      class[i] <- which.max(posterior[i,])
  }
  return(prediction = class)
} 

pp <- nb_test(model = model, test_data = test_1[,-1])
mean(pp == test_1[,1])
```

#read train and test files function:
```{r}
read_files <- function(num_nameset){
  
  #input: which nameset to read (indicated by number)
  #output: 10 experiments train and test data set for that nameset
  
  trainset <- paste("/train_", num_nameset, ".csv", sep = "")
  testser <- paste("/test_", num_nameset, ".csv", sep = "")
  
  train_files <- NULL
  for(i in 1:10){
    file_dir <- paste("/Users/ouminamikun/Documents/Columbia/Spring 2017/ADS/Spr2017-proj4-team-14/output/Exp",i,trainset,sep = "")
    train_files[[i]] <- read.csv(file_dir, header = T)
  }

  test_files <- NULL
  for(i in 1:10){
    file_dir <- paste("/Users/ouminamikun/Documents/Columbia/Spring 2017/ADS/Spr2017-proj4-team-14/output/Exp",i,trainset,sep = "")
    test_files[[i]] <- read.csv(file_dir, header = T)
  }
  return(list(train_files = train_files,test_files = test_files))
}
```

#experiments function
```{r}
experiment <- function(train_files, test_files){
  
  #input: 10 experiments train sets and test sets of one nameset
  #output: the mean and standard deviation of accuracy
  
  model <- NULL
  prediction <- NULL
  accuracy <- NA
  for(i in 1:10){
    train_x <- as.matrix(train_files[[i]][,-1])
    train_y <- train_files[[i]][,1]
    model[[i]] <- nb_train(train_x, train_y)
    prediction[[i]] <- nb_test(model[[i]], test_files[[i]][,-1])
    accuracy[i] <- mean(prediction[[i]] == test_files[[i]][,1])
  }
  return(list(mean = mean(accuracy), StdDev = sd(accuracy)))
}
```

#conduct 10 experiments on the first nameset
```{r}

train_files <- NULL
for(i in 1:10){
  file_dir <- paste("/Users/ouminamikun/Documents/Columbia/Spring 2017/ADS/Spr2017-proj4-team-14/output/Exp",i,"/train_1.csv",sep = "")
  train_files[[i]] <- read.csv(file_dir, header = T)
}

test_files <- NULL
for(i in 1:10){
  file_dir <- paste("/Users/ouminamikun/Documents/Columbia/Spring 2017/ADS/Spr2017-proj4-team-14/output/Exp",i,"/test_1.csv",sep = "")
  test_files[[i]] <- read.csv(file_dir, header = T)
}

model <- NULL
prediction <- NULL
accuracy <- NA
for(i in 1:10){
  train_x <- as.matrix(train_files[[i]][,-1])
  train_y <- train_files[[i]][,1]
  model[[i]] <- nb_train(train_x, train_y)
  prediction[[i]] <- nb_test(model[[i]], test_files[[i]][,-1])
  accuracy[i] <- mean(prediction[[i]] == test_files[[i]][,1])
}
mean(accuracy)
sd(accuracy)
```
#conduct 10 experiments for all namesets
```{r}
accuracy_table <- matrix(NA,2,14)
for(i in 1:14){
  nameset <- read_files(i)
  result <- experiment(nameset$train_files, nameset$test_files)
  accuracy_table[1,i] <- result$mean
  accuracy_table[2,i] <- result$StdDev
}

write.csv(accuracy_table, "accuracy_table.csv")
```


